\problemname{The Library}
You work at a library and want to put a number of books back on the shelves.
The shelves are placed along the $x$-axis.
Given the shelf where each book belongs (an $x$-coordinate between $-1000$ and $1000$) and the maximum number of books you can carry at the same time, determine the shortest distance you must walk to put back all the books.
You and the books to be put back are initially at position $0$.
You do not need to walk back after putting back the last book.

\section*{Input}
The first line contains the integers $N$ and $K$ ($1 \leq N, K \leq 100$),
the number of books to be put back and the number of books you can carry at the same time.

The following $N$ lines each contain an integer $x_i$ ($-1000 \leq x_i \leq 1000$),
the $x$-coordinate of the shelf where each book belongs.

\section*{Output}
Print an integer: the minimum distance you must walk to put back all the books.

\section*{Scoring}
Your solution will be tested on a set of test groups.
To earn points for a group, you must pass all test cases in that group.

\noindent
\begin{tabular}{| l | l | p{12cm} |}
  \hline
  \textbf{Group} & \textbf{Points} & \textbf{Constraints} \\ \hline
  $1$    & $30$        & $K = 1$ \\ \hline
  $2$    & $70$        & No additional constraints. \\ \hline
\end{tabular}

\section*{Explanation of Sample}
For example, you can start by bringing the books that belong on shelves $3$ and $4$.
Then you fetch the book that belongs on shelf $1$, and finally you take the book that belongs on shelf $-4$.
